---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab report #1

Follow the instructions posted at https://ds202-at-isu.github.io/labs.html for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.  

All submissions to the github repo will be automatically uploaded for grading once the due date is passed.
Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.

```{r}
# install.packages("remotes")
library(remotes)
# remotes::install_github("heike/classdata")
library('classdata')
data("ames")
```

## Step 1

```{r}
head(ames)
```


```{r}
str(ames)
```

Variables: 

  Parcel ID (chr): 
    ID of the unit
    Range: ID can be random so no real range
  
  Address (chr):
    Address of the unit
    Range: No real range
  
  Style (Factor): 
    Style of the unit
    Range: No real range
  
  Occupancy (Factor):
    Type of occupancy
    Range: No real range

  Sale Date (Date):
    When unit was put up for sale
    Range: Can be any date
  
  Sale Price (num): 
    Price of the unit
    Range: Approximate Numerical range (50000 - Any Price)
    
  Multi Sale (chr): NA 

  YearBuilt (num): 
    Year the unit was built 
    Range: Approximate Numerical range (1800 - 2026)
  
  Acres (num): 
    Acres of the unit
    Range: Approximate Numerical range (0.1 - 0.9)

  TotalLivingArea (num): 
    Living area
    Range: Approximate Numerical range (500 - 2000)

  Bedrooms (num): 
    Number of bedrooms
    Range: Approximate Numerical range (1 - 6)
    
  FinishedBsmtArea (num):
    Basement area
    Range Approximate Numerical range (400 - 1200)
    
  LotArea (num): 
    Area of the lot 
    Range: Approximate Numerical range (2000 - 16000)

  AC (chr): 
    Does the unit have AC?
    Range : Yes or no
  
  FirePlace (chr): 
    Does the unit have a Fireplace?
    Range : Yes or no

  Neighborhood (Factor):
    What is the neighborhood
    Range : Yes or no

## Step 2

We picked Sale Price as the main variable

## Step 3

```{r}
range(ames$`Sale Price`, na.rm = TRUE)
```
Min : 0
Max : 20500000

```{r}
library(ggplot2)
ggplot(ames, aes(x = `Sale Price`)) + geom_histogram(bins = 50) + scale_x_log10()
```
The histogram is scaled in the above figure

## Step 4




