---
output: github_document
editor_options: 
  markdown: 
    wrap: 72
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab report #1

Follow the instructions posted at
<https://ds202-at-isu.github.io/labs.html> for the lab assignment. The
work is meant to be finished during the lab time, but you have time
until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it
knits properly (into the md file). Upload both the Rmd and the md file
to your repository.

All submissions to the github repo will be automatically uploaded for
grading once the due date is passed. Submit a link to your repository on
Canvas (only one submission per team) to signal to the instructors that
you are done with your submission.

```{r}
# install.packages("remotes")
library(remotes)
# remotes::install_github("heike/classdata")
library('classdata')
data("ames")
```

## Step 1

```{r}
head(ames)
#View(ames)
```

```{r}
str(ames)
```

Variables:

-   Parcel ID (chr): ID of the unit Range: ID can be random so no real
    range

-   Address (chr): Address of the unit Range: No real range

-   Style (Factor): Style of the unit Range: No real range

-   Occupancy (Factor): Type of occupancy Range: No real range

-   Sale Date (Date): When unit was put up for sale Range: Can be any
    date

-   Sale Price (num): Price of the unit Range: Approximate Numerical
    range (50000 - Any Price)

-   Multi Sale (chr): NA

-   YearBuilt (num): Year the unit was built Range: Approximate
    Numerical range (1800 - 2026)

-   Acres (num): Acres of the unit Range: Approximate Numerical range
    (0.1 - 0.9)

-   TotalLivingArea (num): Living area Range: Approximate Numerical
    range (500 - 2000)

-   Bedrooms (num): Number of bedrooms Range: Approximate Numerical
    range (1 - 6)

-   FinishedBsmtArea (num): Basement area Range Approximate Numerical
    range (400 - 1200)

-   LotArea (num): Area of the lot Range: Approximate Numerical range
    (2000 - 16000)

-   AC (chr): Does the unit have AC? Range : Yes or no

-   FirePlace (chr): Does the unit have a Fireplace? Range : Yes or no

-   Neighborhood (Factor): What is the neighborhood Range : Yes or no

## Step 2

We picked **Sale Price** as the main variable, due to its wide range and
approximation to an easily understandable unit of dollars.

## Step 3

```{r}
range(ames$`Sale Price`, na.rm = TRUE)
```

Min : 0 Max : 20500000

```{r}
library(ggplot2)
ames |> ggplot(aes(x = `Sale Price`)) + 
  geom_histogram(bins = 50) +
  ggtitle("Nonscaled Histogram of Sales Price (50 Bins)")
```

```{r}
library(ggplot2)
ames |> ggplot(aes(x = `Sale Price`)) + 
  geom_histogram(bins = 50) + 
  scale_x_log10() +
  ggtitle("Log-Scaled Histogram of Sales Price (50 Bins)")
```

The histogram shows that most houses are sold in the lower price ranges,
while very few houses are sold at very high prices. This has resulted in
a skewed distribution, where a majority of the houses are priced at.

Some unusual is that there are some extremely high prices when compared
to the general range and prices in the data.

Some other anomalous behavior includes unexpectedly low numbers or 0s for sales price, which surely will have impact on further analysis.

## Step 4

#### Acres (Praneet)
```{r}
range(ames$Acres, na.rm = TRUE)
summary(ames$Acres, na.rm = TRUE)
```
```{r}
ggplot(ames, aes(x = Acres)) + geom_histogram(bins = 15)
```
This is a right skewed distribution. Most of the data is concentrated
from 0 to 1, outliers at around 8 and 12 acres. Majority of the observations 
have very small amount of acres.

```{r}
ggplot(ames, aes(x = Acres, y = ames$`Sale Price`)) + geom_point(alpha = 0.4)
```

The scatterplot shows the relationship between 2 variables, Acres and Sale Price. 
There is no clear positive relationship between the 2 variables. Points are concentrated
at around 0-1 acres. This is a weak correlation. Data is very cluttered at the bottom left
corner.

#### Total Living Area (Nikhil)

```{r}
range(ames$`TotalLivingArea (sf)`, na.rm = TRUE)
summary(ames$`TotalLivingArea (sf)`)
```

```{r}
ggplot(ames, aes(x = `TotalLivingArea (sf)`)) +geom_histogram(bins = 30)
```

This is the histogram of the same

```{r}
ggplot(ames, aes(x = `TotalLivingArea (sf)`, y = `Sale Price`)) + geom_point(alpha = 0.4)
```

The scatterplot shows the relationship bw the 2 variables. This appears
to be a positive relationship, meaning higher price would genrally infer
a larger area. However it should be noted that there are some extreme
outliers in this data which skew it a little as evidenced in the top
most and right most areas of the above graph

#### Year Built (Sravya)
```{r}
library(classdata)
library(ggplot2)

data(ames)

ggplot(subset(ames, `YearBuilt` > 1800),
       aes(x = `YearBuilt`, y = `Sale Price`)) +
  geom_point(alpha = 0.5) +
  labs(
    title = "Sale Price vs Year Built",
    x = "Year Built",
    y = "Sale Price ($)"
  )
```

The variable Year Built ranges from about 1870 to around 2020 after removing the invalid value of 0. The scatterplot of Sale Price vs Year Built shows a slight positive relationship, meaning that houses built more recently tend to have higher sale prices. Most homes are concentrated between about 1950 and 2010 with moderate prices. However, there are a few clear outliers where houses built around the early 2000s have extremely high sale prices compared to the rest. These outliers help explain some of the unusually high values that appeared in the histogram of Sale Price in Step 3.

#### Style (Alina)

#### Sale Date (Noam)

``` {r}
range(ames$`Sale Date`)

ames |> ggplot(aes(x = `Sale Date`)) + 
  geom_histogram(bins = 150) + 
  ggtitle("Nonscaled Histogram of Sale Date (50 Bins)")
```
Range of about 5 years, starting mid 2017 to late 2022, Gaps in Q3/4 2019 and 2020. Mostly consistent, with a few dates representing outliers.
``` {r}
ames |> 
  ggplot(aes(x = `Sale Date`, y = `Sale Price`,)) +
  geom_point(alpha = .75, na.rm = TRUE) +
  coord_cartesian(ylim =  c(0, 2000000)) +
  ggtitle("Nonscaled Scatterplot of Sale Date & Sale Price (Lim $2m)")
```
There isn't any great trend to be spotted here, or even a consistent general rise in price over time which may be expected in more extreme economic circumstances. Generally, we are seeing an increase of the ceiling of price per week/month within each year, though the majority stay in the >$50,000 range. There are also many 0s (or roundable 0s) which are easily spotted here and as mentioned in part 3.